A Computational Account of Default-Mode Function\\ by Control Theory and Reinforcement Learning

### 2016-09-29 paper/paper.tex
more

\section{Reinforcement-Learning (RL) as a computational model for DMN function}
\subsection{General RL theory}
In a general reinforcement-learning (RL) framework, an \textit{agent} interacts with an unknown
environment by taking \textit{actions / decisions} $a_t$ which trigger changes in the
\textit{state} of the environment
$s_t \rightarrow s_{t+1}$, accompanied with a real-valued \textit{reward} $r_t$ (or regret!,
since it can be
negative). This should be thought of as an instantaneous satisfaction accompanying the execution of
an action. Here the subscript $t$ denotes time, and can be discrete or continuous.
%% The unknown environment $\mathcal E$ is generally taken as stochastic, but having some kind of
%% memory.
A popular abstract model for the scenario are so-called \textit{Markov Decision Processes (MDPs)}.
This is simply a quintuplet $(\mathcal S, \mathcal A, r, \rho, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, e.g $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $\mathcal A$ is the set of actions, e.g $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{empathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$, so that $r(s, a)$ is the instant reward for taken action $a$ at state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts-off in state $s$.
  \item $\rho : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1]$, so that
    $\rho(s,a,s') = \mathbb P(s'|s, a)$ is the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such transitions be Markovian.
\end{itemize}

>>>>

\section{Reinforcement-Learning as a computational model for DMN function}
\subsection{General Reinforcment-Learning (RL) theory}
In a general reinforcement-learning (RL) framework, an \textit{agent} interacts with an unknown
environment by taking \textit{actions / decisions} $a_t$ which trigger changes in the
\textit{state} of the environment
$s_t \rightarrow s_{t+1}$, accompanied with a real-valued \textit{reward} $r_t$ (or regret!,
since it can be
negative). This should be thought of as an instantaneous satisfaction accompanying the execution of
an action. Here the subscript $t$ denotes time, and can be discrete or continuous.
%% The unknown environment $\mathcal E$ is generally taken as stochastic, but having some kind of
%% memory.
A popular abstract model for the scenario are so-called \textit{Markov Decision Processes (MDPs)}.
This is simply a quintuplet $(\mathcal S, \mathcal A, r, \rho, \mu)$ where
\begin{itemize}
\item $\mathcal S$ is the set of states, e.g $\mathcal S = \{\text{happy}, \text{sad}\}$.
\item $\mathcal A$ is the set of actions, e.g $\mathcal A = \{\text{read}, \text{run},
  \text{laugh}, \text{empathize}, \text{empathize}\}.$
\item $r : \mathcal S \times \mathcal A \rightarrow \mathbb R$, so that $r(s, a)$ is the instant reward for taken action $a$ at state $s$.
\item $\mu: \mathcal S \rightarrow [0, 1]$ is the prior probability on the states so that
  $\mu(s)$ is the probability that the environment starts-off in state $s$.
  \item $\rho : \mathcal S \times \mathcal A \times \mathcal S \rightarrow [0, 1]$, so that
    $\rho(s,a,s') = \mathbb P(s'|s, a)$ is the probability of moving to state $s'$ if action $a$ is taken from state $s$. In addition, one requires that such transitions be Markovian.
\end{itemize}
